# Positioning groups in relation to each other.

This analysis aims to examine how groups may or may not be related to each 
other, noting that each submission expresses itself through a set of things to 
say. This analysis:

- Extracts the word vectors for each submission
- removes the stopwords
- weights the features in each document by the relative term frequency and the
  inverse document frequency - this gives more weight to terms that occur in
  fewer documents and more times in the same document
- represents a group by the sum of all of the document vectors for submissions
  assigned to that group
- calculates the similarity between groups using the cosine similarity, high
  cosine similarity means that the documents in each group 
- Plots the heatmap of similarities, along with the complete linkage based
  dendrogram of clusters using the cosine distance as a pseudo-metric

```{r eval=FALSE}
install.packages("quanteda")
install.packages("quanteda.textstats")
install.packages("RSQLite")
install.packages("writexl")
install.packages("tidyverse")
install.packages("pheatmap")
```

# Load and prepare are submission data as extracted from the various inquiries
```{r}
library(DBI)
library(tidyverse)
library(quanteda)
library(quanteda.textstats)
library(writexl)
library(xtable)
library(pheatmap)

inquiries <- dbConnect(RSQLite::SQLite(), "../inquiries/inquiries.db")
submissions <- dbGetQuery(inquiries, 
  'SELECT submission.*, submission_label.label, context FROM submission
  inner join submission_label using(inquiry_shortname, submission_id)
  inner join inquiry using(inquiry_shortname)
  where priority = 1
  '
) %>% mutate(text = gsub("[‘’]", "'", text))

# Generate a single column unique id - this is the composite primary key
# defined in the database, so will always be unique. This is used to tie
# together results at different granularities.
submissions$doc_id <- paste(submissions$inquiry_shortname, submissions$submission_id)
submission_corpus <- corpus(submissions, text_field="text", docid_field = "doc_id")

dbDisconnect(inquiries)

```

# Groupwise similarity of documents.

The aim of this analysis is pool all documents in a group together and represent
them by the average vector of the bag of words for each document. This will
provide a high level overview of how the language used by each group is similar
to, or dissimilar to, other groups.

```{r}

# These are the byproducts of extracting text from the PDF where images are
# included.
pdf_processing_words <- c(
  'image',
  'height',
  'width',
  'rgb',
  'srgb',
  'bpc',
  '16',
  'iccbased'
)

# Unlike the keyword analysis, we'll include genre words and only remove the
# predefined stoplist and the images in pdf byproduct words.
extended_stopwords <- c(
  pdf_processing_words,
  stopwords("english")
)

submission_tokens <- tokens(
    submission_corpus, remove_punct=TRUE, split_hyphens = TRUE, remove_symbols = TRUE
  ) %>% 
  tokens_remove(extended_stopwords, min_nchar=2)

# Unlike the submissions analysis, we're going to use tf-idf weighting here.
# Each vector will be normalised to unit length, removing the overweighting of 
# the long documents in the process.
submissions_dfm <- dfm(submission_tokens) %>% 
  dfm_tfidf(scheme_tf="prop", scheme_df = "inverse")


# Create groups - note this won't normalise the vectors for each group, that
# will be taken care of by the cosine similarity. Note that force=TRUE is 
# necessary because group vectors are accumulated by summing - if we weren't
# using a similarity method that took into account normalisation of document 
# lengths this would not be appropriate.
groups_dfm <- dfm_group(submissions_dfm, groups = label, force=TRUE)

# Actually calculate the cosine similarity - this is in the quanteda textstats
# format and will need to be converted to a matrix for other functions in some
# cases.
group_similarity <- textstat_simil(groups_dfm, method="cosine")
group_sim_matrix <- as.matrix(group_similarity)

# Create dendrogram from cosine "distance" to use for ordering the rows and cols
# of the heatmap.
hclust_res <- hclust(as.dist(1 - group_sim_matrix))  # 1 - cosine_similarity for distance

group_names <- c(
 "commercial, non con", "agricultural", "electedrep", "environmental", 
 "first nations", "government", "not categorisable", "regional", "research", 
 "resource managers"
)

pheatmap(
  group_sim_matrix, cluster_rows=hclust_res, cluster_cols=hclust_res, 
  angle_col=45, display_numbers = round(group_sim_matrix, 2),
  cellwidth = 24, cellheight = 24, 
  main = "Group Similarities",
  filename = "../results/groupwise_heatmap.pdf",
  width = 5.5, height = 5.5,
  legend = FALSE
)


```



 