# Concordance with document level annotations

This notebooks prepares concordances for a specified set of keywords, and annotates
them with document level statistics - a submission that mentions "unfair" is
more likely to be useful as a whole than a document with just a single mention
of one of the keywords.

## Install dependencies

This only needs to be run once.

```{r eval=FALSE}
install.packages("quanteda")
install.packages("RSQLite")
install.packages("writexl")
```

# Load Libraries

Note that this is intentionally a minimal script so we aren't actually going
to do much outside loading data and some light transformation.

```{r}
library(DBI)
library(quanteda)
library(writexl)
```
# Connect and load from the database

```{r}
inquiries <- dbConnect(RSQLite::SQLite(), "../inquiries/inquiries.db")
submissions <- dbGetQuery(inquiries, 
  'SELECT submission.*, submission_label.label FROM submission
  inner join submission_label using(inquiry_shortname, submission_id)
  where priority = 1
  '
)

# Generate a single column unique id - this is the composite primary key
# defined in the database, so will always be unique. This is used to tie
# together results at different granularities.
submissions$doc_id <- paste(submissions$inquiry_shortname, submissions$submission_id)
submission_corpus <- corpus(submissions, text_field="text", docid_field = "doc_id")

dbDisconnect(inquiries)

print(submission_corpus)
```

# Prepare Concordances

We're going to create two output files for closer reading:

1. A file of concordances, showing where each of the selected keywords occurs
in each file, along with the context of which file they came from.
2. A file describing how many times each keyword is used in each file, to enable
sorting for documents that mention the keywords many times. 

```{r}
general_probes = c(
  "equity",
  "equitable",
  "inequitable",
  "inequity",
  "fair",
  "unfair",
  "fairness",
  "unfairly",
  "fairly",
  "just",
  "justice",
  "injustice",
  "unjust"  
)

trust_probes = c(
  "trust",
  "mistrust",
  "trustworthy",
  "lies",
  "lying",
  "fraud",
  "theft",
  "greed",
  "greedy",
  "deceived",
  "deceitful",
  "confidence",
  "mislead",
  "misled",
  "misleading",
  "misinformation",
  "disinformation",
  "misinformed",
  "disinformed",
  "faith"
)


make_concordances <- function(corpus, probe_words){
  # Tokenise and prepare the DFM - note we're leaving the text more or less for
  # now as we're only interested in a token count and raw concordances.
  corpus_tokens <- tokens(corpus)
  corpus_dfm <- dfm(corpus_tokens)
  
  # Select columns of the probe words - this is for sorting the submissions table.
  probe_counts <- dfm_select(corpus_dfm, pattern = probe_words) %>% convert(to = "data.frame")
  
  # Create the concordances for selected words
  concordances <- kwic(corpus_tokens, probe_words, window=25) %>% as.data.frame()
  
  concordances$merged <- paste(concordances$pre, concordances$keyword, concordances$post)
  
  # Merge the concordances with the document level count for sorting.
  # Also add the document level variables
  submissions[,c("doc_id", "url", "submitter", "inquiry_shortname", "label")] %>%
    merge(probe_counts, by="doc_id") %>%
    merge(concordances, by.x = "doc_id", by.y = "docname")
}

concordance_with_agg <- make_concordances(submission_corpus, general_probes)
write_xlsx(concordance_with_agg, "../results/general_concordance_with_doc_agg.xlsx")

concordance_with_agg <- make_concordances(submission_corpus, trust_probes)
write_xlsx(concordance_with_agg, "../results/trust_concordance_with_doc_agg.xlsx")

```

```



```


