---
title: "Extended Moral Foundations Dictionary Scoring of Submissions by Inquiry"
output: html_notebook
---

```{r eval=FALSE}
install.packages("RSQLite")
install.packages("writexl")
```

```{r}
library(DBI)
library(ggplot2)
library(tidyverse)
```

# Average EMFD scores by inquiry

Compute average score for each moral foundation for submissions to each inquiry.
Note that we're filtering out any submission that doesn't use any moral words
at all with the `moral_nonmoral_ratio` variable - this is important because some
of the submissions have very few words, (or no words at all if they haven't been
OCR'ed yet) - if we included these we would be underestimating the score because
have a 0 default score. The Moral Foundation scores are based on the paper below
using the Extended Moral Foundations Dictionary.

Hopp, F.R., Fisher, J.T., Cornell, D. et al. The extended Moral Foundations
Dictionary (eMFD): Development and applications of a crowd-sourced approach
to extracting moral intuitions from text. Behav Res 53, 232–246
(2021). https://doi.org/10.3758/s13428-020-01433-0

```{r}
inquiries <- dbConnect(RSQLite::SQLite(), "../inquiries/inquiries.db")

label_scores <- dbGetQuery(inquiries, 
  "
  select inquiry_shortname, submission_id, label, score_type, score
  from submission_emfd_score
  inner join submission_label using(inquiry_shortname, submission_id)
  where score_type != 'moral_nonmoral_ratio'
    and priority = 1
  ;"                          
)

dbDisconnect(inquiries)

head(label_scores)
```

# EMFD scores by submitter label

```{r}
# p2 <- dbGetQuery(inquiriesDB, "SELECT * FROM submission_emfd_score WHERE inquiry_shortname = 'select_committee_fph_2021'") %>%
# inner_join(select_committee_fph_2021_coding_long, by = c("submission_id" = "id")) %>% #join DB to coded data
#   filter(rank == 1, !score_type == "moral_nonmoral_ratio") %>% #filter by first group coded (i.e. rank=1 and remove moral_nonoral_ratio
#   select("submitterType", "submission_id", "score_type", "score") %>% 
# group_by(score_type, submitterType) %>%
# summarise(score_average = mean(score)) %>% # calculate average after grouping

label_plot <- label_scores %>%
  ggplot(aes(x = score, y = label)) + # chart
  geom_jitter(height=0.4, size=0.1) +
  facet_wrap(~score_type, ncol = 2) +
 geom_vline(xintercept = 0, color = "#FFCCCC", size = 0.5) + # create easy to see zero line
  theme_minimal() #change theme to a simpler one

ggsave("emfdBySubmitterType.pdf", plot = label_plot, width = 11, height = 8.5)

```

```{r}

```

