---
title: "Extended Moral Foundations Dictionary Scoring of Submissions by Inquiry"
output: html_notebook
---

```{r eval=FALSE}
install.packages("RSQLite")
install.packages("writexl")
```

```{r}
library(DBI)
library(ggplot2)
```

# Average EMFD scores by inquiry

Compute average score for each moral foundation for submissions to each inquiry.
Note that we're filtering out any submission that doesn't use any moral words
at all with the `moral_nonmoral_ratio` variable - this is important because some
of the submissions have very few words, (or no words at all if they haven't been
OCR'ed yet) - if we included these we would be underestimating the score because
have a 0 default score. The Moral Foundation scores are based on the paper below
using the Extended Moral Foundations Dictionary.

Hopp, F.R., Fisher, J.T., Cornell, D. et al. The extended Moral Foundations
Dictionary (eMFD): Development and applications of a crowd-sourced approach
to extracting moral intuitions from text. Behav Res 53, 232–246
(2021). https://doi.org/10.3758/s13428-020-01433-0

```{r}
inquiries <- dbConnect(RSQLite::SQLite(), "../inquiries/inquiries.db")
submission_scores <- dbGetQuery(inquiries, 
  "with submission_any_moral_word as (
  	select 
  		inquiry_shortname, 
  		submission_id 
  	from submission_emfd_score 
  	where score_type = 'moral_nonmoral_ratio' 
  		and score > 0
  ) 
  select score_type, inquiry_shortname, avg(score) as score
  from submission_emfd_score
  inner join submission_any_moral_word using(inquiry_shortname, submission_id)
  where score_type != 'moral_nonmoral_ratio'
  group by inquiry_shortname, score_type
  ;"                          
)

dbDisconnect(inquiries)

head(submission_scores)
```

# EMFD scores by inquiry

```{r}
# Plot by score for each inquiry to show per inquiry differences
ggplot(
  data = submission_scores, 
  mapping = aes(y = inquiry_shortname, x = score)
) + geom_point() + facet_wrap(vars(score_type), ncol = 2)

```



